---
title: 'Your Title Here'
author: "Don Francisco"
date: "August 27, 2019"
output: word_document
csl: bioinformatics.csl
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

# Methods

## Study design

## Analysis

# Results

## Subsections are ok in the results section too

```{r load-libraries}
library("ggplot2")
library("dplyr")
library("tidyr")
library("readr")
```

```{r read-in-culture-data}
# read in the culture data from csv
culture_data <- read_csv(
  "data/raw_data/Raw_culture_count_data/Culturing_data.csv")
```

```{r filter-and-plot-abundances}
# filter out only my 100x dilutions and make a boxplot
culture_data %>%
  filter(student_name == "Kris Choi") %>%
  filter(dilution_1_10_or_100 == "1") %>%
  ggplot(aes(x = sample_group,
             y = number_of_colonies)) +
  geom_boxplot() +
  ggtitle(paste("Comparison of colony abundances between refrigerated and", 
  "room temperature
storage conditions, 1x dilution")) +
  xlab("Sample Group") +
  ylab("Number of colonies")
```

**Figure 1:** Boxplot of colony abundances at different storage conditions, 
1x dilution. Despite a higher median number of colonies from room temperature 
samples, the mean numbers of colonies were not significantly different between 
the two storage conditions (Wilcox p = 0.0636).

```{r abundances-stats}
# run a statistical test to compare the two groups of abundances
culture_data %>%
  filter(student_name == "Kris Choi") %>%
  filter(dilution_1_10_or_100 == "1") %>%
  wilcox.test(data = .,
              number_of_colonies ~ sample_group)
```



```{r filter-and-plot-morphotypes}
# filter out only my 100x dilutions and make a boxplot
culture_data %>%
  filter(student_name == "Kris Choi") %>%
  filter(dilution_1_10_or_100 == "1") %>%
  ggplot(aes(x = sample_group,
             y = as.numeric(number_of_morphotypes))) +
  geom_boxplot() +
  ggtitle(paste("Comparison of colony morphotypes between refrigerated and", 
  "room temperature
storage conditions, 1x dilution")) +
  xlab("Sample Group") +
  ylab("Number of Morphotypes")
```


**Figure 2:** Boxplot showing the number of morphotypes from the two different storage conditions. There was no difference in the mean number of morphotypes (Wilcox p=0.19).


```{r morphotypes-stats}
# run a statistical test to compare the two groups of morphotypes
culture_data %>%
  filter(student_name == "Kris Choi") %>%
  filter(dilution_1_10_or_100 == "1") %>%
  wilcox.test(data = .,
              as.numeric(number_of_morphotypes) ~ sample_group)
```

# Discussion

# Sources Cited
